---
title: "`r paste0('NanoQuRe Sequencing QC Report - Multiple Samples')`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: paper      
    highlight: pygments    
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_folding: hide
params:
  data: NULL
---

<style>
  h1.title { color: #612a78 !important; font-weight: bold; }
  h4.author, h4.date, .subtitle { color: #333333; font-weight: normal; }
  h2, h3 { color: #2c3e50; font-weight: bold; }
  .list-group-item.active, 
  .list-group-item.active:focus, 
  .list-group-item.active:hover {
    background-color: #612a78 !important;
    border-color: #612a78 !important;
    color: white !important;
  }
</style>

```{r setup, include=FALSE}
library(NanoQuRe)
library(dplyr)
library(ggplot2)
library(htmltools) # Required to render lists of interactive HTML widgets

samples_split <- split(params$data, params$data$sample_id)
```

## Sequencing Statistics Table
```{r, echo=FALSE}
lapply(samples_split, sequencing_stats) %>%
  dplyr::bind_rows() %>%
  DT::datatable(caption = 'Table 1: Sequencing Summary Statistics')
```


## Quality Statistics Table
```{r, echo=FALSE}
lapply(samples_split, quality_stats) %>%
  dplyr::bind_rows() %>%
  DT::datatable(caption = 'Table 2: Sequencing Summary Quality Statistics')
```

## Read Lengths
```{r, echo=FALSE}
htmltools::tagList(lapply(samples_split, plot_read_lengths))
```

## Cumulative Yield
```{r, echo=FALSE}
htmltools::tagList(lapply(samples_split, plot_cumulative_yield))
```

## Quality Distribution
```{r, echo=FALSE}
htmltools::tagList(lapply(samples_split, plot_quality_distribution))
```

## Translocation Speed
```{r, echo=FALSE}
htmltools::tagList(lapply(samples_split, plot_average_speed))
```

## Sequencing Throughput
```{r, echo=FALSE}
htmltools::tagList(lapply(samples_split, plot_seq_throughput))
```

## Channel Activity
```{r, echo=FALSE}
htmltools::tagList(lapply(samples_split, plot_active_channels))
```

## Length and Qscore
```{r, echo=FALSE}
htmltools::tagList(lapply(samples_split, function(s) {
  double_results <- plot_double(s)
  htmltools::tagList(double_results$length_plot, double_results$qscore_plot)
}))
```

