---
title: "`r paste0('NanoQuRe Sequencing QC Report ', dplyr::first(params$data$sample_id))`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: paper      
    highlight: pygments    
    toc: true           #Table of content
    toc_float:
      collapsed: false  # This keeps the menu open so you see all plots
      smooth_scroll: true # Makes the transition "glide" when clicked
    code_folding: hide
params:
  data: NULL
---

<style>
  /* 1. Only the main title (h1) in purple */
  h1.title { color: #612a78 !important; font-weight: bold; }
  
  /* 2. The subtitle (sample name) stays dark/neutral */
  h4.author, h4.date, .subtitle { color: #333333; font-weight: normal; }

  /* 3. Headers (h2, h3) stay neutral/dark for a minimalist look */
  h2, h3 { color: #2c3e50; font-weight: bold; }

  /* 4. Only the active (selected) item in the Table of Contents is purple */
  .list-group-item.active, 
  .list-group-item.active:focus, 
  .list-group-item.active:hover {
    background-color: #612a78 !important;
    border-color: #612a78 !important;
    color: white !important;
  }
</style>


```{r setup, include=FALSE}
library(NanoQuRe)
library(dplyr)
library(ggplot2)
```




## Sequencing Statistics Table
```{r, echo=FALSE}
DT::datatable(sequencing_stats(params$data), caption = 'Table 1: Sequencing Summary Statistics')
```




## Quality Statistics Table
```{r, echo=FALSE}
DT::datatable(quality_stats(params$data), caption = 'Table 1: Sequencing Summary Quality Statistics')
```




## Read Lengths
```{r, echo=FALSE}
plot_read_lengths(params$data)
```




## Cumulative Yield
```{r, echo=FALSE}
plot_cumulative_yield(params$data)
```




## Quality Distribution
```{r, echo=FALSE}
plot_quality_distribution(params$data)
```




## Translocation Speed
```{r, echo=FALSE}
plot_average_speed(params$data)
```




## Sequencing Throughput
```{r, echo=FALSE}
plot_seq_throughput(params$data)
```




## Channel Activity
```{r, echo=FALSE}
plot_active_channels(params$data)
```




## Length and Qscore
```{r, echo=FALSE}
double_results <- plot_double(params$data)
double_results$length
double_results$qscore
```



