---
title: "n50"
output: html_document
---

```{r}
print(type(ligase_ela$sequence_length_template))
as.numeric(ligase_ela$sequence_length_template)
print(type(ligase_ela$sequence_length_template))
```


# Total Bases
```{r}
total_bases <- sum(ligase_induro$sequence_length_template)

```


#Find the length that represents half of your total data. Action: Calculate 50% of the total bases.
```{r}
half_data <- total_bases/2
```

#Sort Sequences Action: Sort all sequence lengths from longest to shortest (descending order).
```{r}
induro_descend_seq <- ligase_induro %>% select(sequence_length_template) %>% arrange(desc(sequence_length_template)) %>% pull(sequence_length_template)
#The function pull selects a column in a data frame and transforms it into a vector.

```

# Calculate Cumulative SumIterate through the sorted lengths to find where the midpoint is passed.Action: Starting with the longest sequence, add the lengths together sequentially.Goal: Continue adding until the running total (the cumulative sum) exceeds or equals half_data
```{r}
induro_cumulative_sum <- cumsum(induro_descend_seq)
in50_index <- which(cumulative_sum >= half_data)[1]
in50_value <- induro_descend_seq[n50_index]

```


```{r}

```




```{r}
n50_calc <- function(my_data){
  total_bases <- sum(my_data$sequence_length_template)
  half_data <- total_bases/2
  descend_seq <- ligase_ela %>% select(sequence_length_template) %>% arrange(desc(sequence_length_template)) %>% pull(sequence_length_template)
  cumulative_sum <- cumsum(descend_seq)
n50_index <- which(cumulative_sum >= half_data)[1]
n50_value <- descend_seq[n50_index]
}
```

```{r}
n50_database <- lapply(seqsum_database, n50_calc)
```

```{r}
induro_n50 <- n50_calc(ligase_induro)
```





